\section{GLM}

BROCCOLI provides a separate function for the general linear model (GLM). A GLM can for a single subject be performed as

\begin{verbatim}
GLM volumes.nii -design design.txt -contrasts contrasts.txt -firstlevel
\end{verbatim}
where volumes.nii is a 4D file containing all volumes from an experiment, design.txt contains all the raw regressors and can for example be defined as

\begin{verbatim}
NumRegressors 2

1.0 0.0
1.0 0.0
1.0 0.0
1.0 0.0
1.0 0.0
0.0 1.0
0.0 1.0
0.0 1.0
0.0 1.0
0.0 1.0
\end{verbatim}
while the contrasts.txt file can be defined as

\begin{verbatim}
NumRegressors 2
NumContrasts 2

1.0 -1.0
-1.0 1.0
\end{verbatim}
\newpage
\noindent For a single subject, the GLM can also be performed as 

\begin{verbatim}
GLM data.nii -designfiles regressors.txt -contrasts contrasts.txt -firstlevel
\end{verbatim}
where regressors.txt can look like

\begin{verbatim}
NumRegressors 3

task1.txt
task2.txt
task3.txt
\end{verbatim}
Each task file needs to include the number of events, the start time of each event, the length of each event and the value for the regressor of each event (this format is very similar to the one used by the FSL software). A task file can for example look like

\begin{verbatim}
NumEvents 8

47.532543       2.517515        1
68.789386       2.950905        1
93.547212       2.934332        1
165.670213      3.584591        1
190.078151      1.817203        1
257.349564      2.584177        1
280.457018      1.367038        1
308.66593       2.084071        1
\end{verbatim}
For all first level analyses, BROCCOLI will automatically add detrending regressors and remove the mean of all the activity regressors. \newline 

\noindent For a group analysis, a GLM can be performed as
\begin{verbatim}
GLM volumes.nii -design design.txt -contrasts contrasts.txt -secondlevel
\end{verbatim}
where volumes.nii is a 4D file containing beta values from each subject.



\section{OpenCL options}

The following OpenCL options are available

\begin{itemize}

\item -platform
\newline \newline The OpenCL platform to use (default 0).

\item -device
\newline \newline The OpenCL device to use (default 0).

\end{itemize}

\section{GLM options}

The following GLM options are available

\begin{itemize}

\item -design
\newline \newline The design matrix to use in the GLM. 

\item -designfiles
\newline \newline The regressors to use in the GLM, each line in the text file points to a task file. 

\item -contrasts                 
\newline \newline The contrast vector(s) to apply to the estimated beta values. 

\item -firstlevel
\newline \newline Do a GLM for a single subject.
 
\item -secondlevel
\newline \newline Do a GLM for several subjects.
 
\item -teststatistics
\newline \newline Test statistics to use, 0 = GLM t-test, 1 = GLM F-test  (default 0).

\item -betasonly
\newline \newline Only save the beta values (no t- or F-test), contrast file not needed (default no)

\item -contrastsonly
\newline \newline Only save the contrast values (default no)

\item -betasandcontrastsonly
\newline \newline Only save the beta values and the contrast values (default no)

\item -mask                      
\newline \newline A mask that defines which voxels to analyze (default none). 
\end{itemize}


\section{Single subject options}

The following single subject options are available

\begin{itemize}

\item -temporalderivatives
\newline \newline Use temporal derivatives for the activity regressors (default no). The contrast vectors will automatically be extended with zeros for these additional regressors. Only possible for -designfiles, not for -design.

\item -regressmotion
\newline \newline Provide a file with motion regressors to use in the design matrix (default no). The file can be generated by FirstLevelAnalysis or MotionCorrection. The contrast vectors will automatically be extended with zeros for these additional regressors.

\item -regressglobalmean
\newline \newline Include global mean in design matrix (default no). The contrast vectors will automatically be extended with zeros for this additional regressor.


\end{itemize}


\section{Outputs}

By default, the GLM function saves each beta value as 

\begin{verbatim}
volumes_beta_regressor001.nii ... volumes_beta_regressorR.nii
\end{verbatim}
for R regressors. For each contrast, BROCCOLI also saves the contrast of parameter estimate (COPE) and the corresponding t-scores, e.g.

\begin{verbatim}
volumes_cope_contrast001.nii  - volumes_cope_contrastC.nii

volumes_tscores_contrast001.nii - volumes_tscores_contrastC.nii
\end{verbatim}

\section{Output options}

The following output options are available

\begin{itemize}


\item -saveresiduals
\newline \newline Save the residuals (default no). 

\item -saveresidualvariance
\newline \newline Save the residual variance (default no).

\item -savearparameters
\newline \newline Save the estimated AR coefficients (first level only, default no).

\item -saveoriginaldesignmatrix
\newline \newline Save the original design matrix used (default no).

\item -savedesignmatrix
\newline \newline Save the total design matrix used (default no).

\item -output 
\newline \newline Set output filename (default volumes\_).

\end{itemize}

\section{Additional options}

The following additional options are available

\begin{itemize}

\item -quiet 
\newline \newline Don't print anything to the terminal (default false). 

\item -verbose
\newline \newline Print extra stuff (default false). 

\end{itemize}


